Alex's Notes and Text Fragments for the JSS Manuscript

### 2021-07-24 paper/paper.Rmd
ask for examples

- Do natural groupings exists in the data?
- How dense are the observations scattered both in space and time?
- Are existing predictor variables known to be highly affected by spatiotemporal autocorrelation by nature?

>>>>

- Do natural groupings exists in the data? <!--Example-->
- How dense are the observations scattered both in space and time?
The closer observations are in space and/or time, the more similar they are, and hence the greater is the effect of spatio-temporal autocorrelation.
- Are some of the predictor variables under consideration known to be highly affected by spatiotemporal autocorrelation such as ... <!-- pls add an example -->?
